---
title: "Lillie Pennington HW4 not regexp"
output:
  html_document:
    df_print: paged
---

```{r}


library(tidyverse)
require(readr)

```

```{r}

o3.filenames <- list.files(pattern = ".txt")
o3.filelist <- lapply(o3.filenames, read_delim, delim = "|")

```

```{r}
names(o3.filelist) <- gsub(".txt","", o3.filenames)

o3.filelist
```

##2. What class is o3.filelist? What does it contain?
It's a list. It contains a list of tibbles from the text files.

##3. Using ~ 1 sentence per line in the above code, explain what each line in the code is doing.
#setwd("air quality")
sets my working directory to where the data is

#o3.filenames <- list.files(pattern = ".txt")
stores the character vector of the names of the .txt files

#o3.filelist <- lapply(o3.filenames, read_delim, delim = "|")
lapply applies the read_delim function to the list of files in o3.filenames

#names(o3.filelist) <- gsub(".txt","", o3.filenames)
the names of the o3.filelist objects have .txt removed from the end

##4. Rewrite the code above using the stringr package insead of grep{base}.
names(o3.filelist) <- str_replace(o3.filenames, ".txt", "")

```{r}
library(data.table)
library(tidyverse)
daily <- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), date) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
daily
```

##5. Rewrite the code above using traditional object-based R programming instead of the piping operator.
```{r}
library(data.table)
library(tidyverse)
 
bfiles <- rbindlist(o3.filelist)
gfiles <-group_by(bfiles, site = as.factor(site), date) 
daily<- summarize(gfiles, o3 = mean(obs, na.rm = TRUE))
daily
```


##6. Summarize the o3 data above by site and by month and by year using a piping operator (the monthly mean o3 for each site for each year).
```{r}
daily <- o3.filelist %>%
  rbindlist() %>%
  mutate(yr = lubridate::year(date)) %>%
  mutate(mo = lubridate::month(date)) %>%
  group_by(site = as.factor(site), yr, mo) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
daily
```

##7. Challenge! Ozone pollution actually follows a very strong diurnal pattern. How would you summarize the daily data from above in a better way to capture that diurnal pattern?
```{r}
hourly <- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), start_hour) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
hourly
```
##8. How many site names in the CA air quality location dataset “Site Name” contain “San” or “Santa?”.
```{r}
library(readxl)
location <- read_excel("location.xls")

sitename <- select(location, "Site Name")
sitename

sum(str_detect(location$`Site Name`, "Santa")) #36
sum(str_detect(location$`Site Name`, "San")) #98

98-36

San = 62, Santa = 36

```

##9. Identify the number of sites that do not have a complete address (full street address and zip code).
```{r}
fulladd <- rbind(location$Address, location$`Zip Code`)
#here's my idea: i bound the address to the zipcode, now i'm trying to detct addresses that start with a number and end with 5...

nonum <- str_detect(fulladd, "^[0-9].*[0-9][0-9][0-9][0-9][0-9]$")

length(nonum[nonum==FALSE])

#1839? seems high...
```

##10. How does a semi join differ from an inner join?
Inner join keeps columns from x and y, semi join just keeps columns from x

##11. Write a function to calculate the annual mean, median, max and min of all sites that have “San” or “Santa” in their name.
```{r}

mmmm <- function(h) {
  mean(h, na.rm = TRUE)
  median(h, na.rm = TRUE)
  max(h, na.rm = TRUE)
  min(h, na.rm = TRUE)
}

#for str_detect(location$`Site Name`, "San") {mmmm}


#idk erin.. 


```

##12. Write a function to caculate the annual daily mean. Apply that function to Merced County. What is the annual daily mean of o3 for Merced County?
```{r}
yearly <- o3.filelist %>%
  rbindlist() %>%
  mutate(yr = lubridate::year(date)) %>%
  group_by(site = as.factor(site), yr) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
yearly

mean(yearly$o3)

#0.02942594; i guess i didn't need to group by year

```


