---
title: "Lillie Pennington HW4 not regexp"
output:
  html_document:
    df_print: paged
---

```{r}


library(tidyverse)
require(readr)

```

```{r}
setwd("air quality")

o3.filenames <- list.files(pattern = ".txt")
o3.filelist <- lapply(o3.filenames, read_delim, delim = "|")

```

```{r}
names(o3.filelist) <- gsub(".txt","", o3.filenames)

o3.filelist
```

##2. What class is o3.filelist? What does it contain?
It's a list. It contains a list of tibbles from the text files.

##3. Using ~ 1 sentence per line in the above code, explain what each line in the code is doing.
#setwd("air quality")
sets my working directory to where the data is

#o3.filenames <- list.files(pattern = ".txt")
stores the character vector of the names of the .txt files

#o3.filelist <- lapply(o3.filenames, read_delim, delim = "|")
lapply applies the read_delim function to the list of files in o3.filenames

#names(o3.filelist) <- gsub(".txt","", o3.filenames)
the names of the o3.filelist objects have .txt removed from the end

##4. Rewrite the code above using the stringr package insead of grep{base}.
names(o3.filelist) <- str_replace(o3.filenames, ".txt", "")

```{r}
library(data.table)
library(tidyverse)
daily <- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), date) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
daily
```

##5. Rewrite the code above using traditional object-based R programming instead of the piping operator.
```{r}
library(data.table)
library(tidyverse)
 
bfiles <- rbindlist(o3.filelist)
gfiles <-group_by(bfiles, site = as.factor(site), date) 
daily<- summarize(gfiles, o3 = mean(obs, na.rm = TRUE))
daily
```


##6. Summarize the o3 data above by site and by month and by year using a piping operator (the monthly mean o3 for each site for each year).
```{r}
daily <- o3.filelist %>%
  rbindlist() %>%
  mutate(yr = lubridate::year(date)) %>%
  mutate(mo = lubridate::month(date)) %>%
  group_by(site = as.factor(site), yr, mo) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
daily
```

##7. Challenge! Ozone pollution actually follows a very strong diurnal pattern. How would you summarize the daily data from above in a better way to capture that diurnal pattern?
```{r}
hourly <- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), start_hour) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
hourly
```
<span style="color:red">Nice! Here is my version :) I didn't put it in ```{r} since we named our datasets a bit different

hourly<- o3.filelist %>%
  rbindlist() %>%
  group_by(site = as.factor(site), start_hour, year(date)) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
#head(hourly)
ggplot(data= hourly)+
  geom_point(mapping=aes(x=start_hour,y=o3)) </span>

##8. How many site names in the CA air quality location dataset “Site Name” contain “San” or “Santa?”.
```{r}
library(readxl)
location <- read_excel("air quality/location.xls")

sum(str_detect(location$`Site Name`, "Santa")) #36
sum(str_detect(location$`Site Name`, "San")) #98

98-36

#San = 62, Santa = 36

```
<span style="color:red">I like how you did #8 in order to address fragility of the code you can create a function that will allow you to chanfe the "San" or "Santa" to other names. I didn't quite do that, but here is one version that I have: 
x <- c("San", "Santa")
name_match <- str_c(x,collapse = "|")
name_subset <- str_subset(loc$`Site Name`,name_match)
count_names <- str_count(name_subset,name_match)
sum(count_names)  </span>

##9. Identify the number of sites that do not have a complete address (full street address and zip code).
```{r}

fulladd <- filter(location, str_detect(location$Address, "^(\\d|PO)")== FALSE
                  & str_detect(location$`Zip Code`, "\\d{5}") == FALSE)

dim(fulladd)
#8 sites do not have a full address 
```

##10. How does a semi join differ from an inner join?
Inner join keeps columns from x and y, semi join just keeps columns from x

##11. Write a function to calculate the annual mean, median, max and min of all sites that have “San” or “Santa” in their name.
```{r}

mmmm <- function(h) {
  mean(h, na.rm = TRUE)
  median(h, na.rm = TRUE)
  max(h, na.rm = TRUE)
  min(h, na.rm = TRUE)
}

#for str_detect(location$`Site Name`, "San") {mmmm}


#idk erin.. 


```
<span style="color:red">I need to debug my code...something is wrong and I could not rerun it! But this is what I have so far: 

site.summary <- function(x,y,z){
  yearly <- x %>%
    group_by(site = as.factor(site))%>%
    mutate(year = format(date, "%Y")) %>%
    group_by(site,year) %>%
    c <- c(y, z)
  name_match <- str_c(c,collapse = "|")
  d <- str_subset(loc$`Site Name`,name_match)
  San <- subset(yearly, yearly$`Site Name`== d )%>%
    group_by(site,year )%>%
    summarize(mean=mean(o3, na.rm=TRUE),median=median(o3, na.rm = TRUE),max=max(o3, na.rm=TRUE),min=min(o3, na.rm=TRUE))
  San
}
site.mean(daily.site,"San","Santa")  </span>

##12. Write a function to caculate the annual daily mean. Apply that function to Merced County. What is the annual daily mean of o3 for Merced County?
```{r}
yearly <- o3.filelist %>%
  rbindlist() %>%
  mutate(yr = lubridate::year(date)) %>%
  group_by(site = as.factor(site), yr) %>%
  summarize(o3 = mean(obs, na.rm = TRUE))
yearly

mean(yearly$o3)

#0.02942594; i guess i didn't need to group by year

```


